Accelerated oblique random survival forests

### 2022-06-14 docs/index.Rmd
moving slides to bonus

Consider the usual framework for survival analysis:
$$\mathcal{D}_{\text{train}} = \left\{ (T_i, \delta_i, x_{i}) \right\}_{i=1}^{N_{\text{train}}}.$$
- $T_i$ is the event time if $\delta_i=1$ and last point of contact if $\delta_i=0$,

@@

Let $t_1 < \, \ldots \, < t_m$ denote the $m$ unique event times in $\mathcal{D}_{\text{train}}$

We identify linear combinations of predictor variables in non-leaf nodes by applying Newton Raphson scoring to the partial likelihood function of the Cox regression model: $$L(\beta) = \prod_{i=1}^m \frac{e^{x_{j(i)}^T \beta}}{\sum_{j \in R_i} e^{x_j^T \beta}}$$

@@

@@

- .rainbow-text[_aorsf-fast_]: the fast version of aorsf

@@

@@

@@

_Presentation_: We scale the IPA by 100 to avoid unnecessary leading zero's.

Step 1: Collect IPA values from ten 50/50 train/test splits on each data set for each learner.

Step 2: Fit a hierarchical Bayesian model to analyze posterior expected IPA values for each learner:

$$\text{IPA} = \widehat{\gamma} \cdot \text{model} + (1\,|\, \text{data/run})$$

where `run` refers to the specific train/test split of `data`.

@@

>>>>

We identify linear combinations of predictor variables in non-leaf nodes by applying Newton Raphson scoring to the partial likelihood function of the Cox regression model: $$L(\beta) = \prod_{i=1}^m \frac{e^{x_{j(i)}^{'} \beta}}{\sum_{j \in R_i} e^{x_j^{'} \beta}}$$

@@

@@

- $t_1 < \, \ldots \, < t_m$ are the $m$ unique event times in the training data.

@@

- .rainbow-text[_aorsf-fast_]: this is the only oblique RSF we show in the racing model plots.

@@

- number of observations ranged from `r min(data_key$nrow)` to `r max(data_key$nrow)` (median = `r median(data_key$nrow)`)

- number of predictors ranged from `r min(data_key$ncol)` to `r max(data_key$ncol)` (median = `r median(data_key$ncol)`)

- % censored ranged from `r round(100*min(data_key$pcens))` to `r round(100*max(data_key$pcens))` (median = `r round(100*median(data_key$pcens))`)

(Full table is shown in the bonus slides)

@@

We measured performance of each learner with:

- index of prediction accuracy (IPA); __higher__ is 👍

- time-dependent concordance (C)-statistic; __higher__ is 👍

- total time to fit a model and compute predictions; __lower__ is 👍

@@

How do we estimate overall performance based on all 23 risk prediction tasks?

Step 1: Collect IPA and C-statistic values:

- For each of the 23 risk prediction problems,

    + split the corresponding data into a 50/50 train/test split
    + fit each learner to the training set
    + evaluate each learner's predictions in the testing set

--

Step 2: Fit a hierarchical Bayesian model to analyze posterior expected performance for each learner:

$$\text{metric} = \widehat{\gamma} \cdot \text{model} + (1\,|\, \text{data/run})$$

- `run` refers to the specific train/test split of `data`

- `metric` is either the IPA or the time-dependent C-statistic.

@@

---
class: center, middle

# .huge[.rainbow-text[BONUS ROUND]]

# Data sets

## Evaluation (bonus round)

## Evaluation (bonus round)

## Evaluation (bonus round)
